NumLin: Linear Types for Linear Algebra

### 2019-05-27 write-up/paper/formal_system.tex
Remove Appendix (cleanly) from rest of paper

The full typing rules are in Appendix \ref{subsec:static_sem}, but the key
ideas are as follow.

@@

The full, small-step transition relation is in Appendix \ref{subsec:dyn_sem},
but the key ideas are as follow.

>>>>

The full typing rules are in Appendix~\ref{subsec:static_sem}, but the key
ideas are as follow.

@@

The full, small-step transition relation is in Appendix~\ref{subsec:dyn_sem},
but the key ideas are as follow.
